Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-07 Papers/ms.tex
Results figures for the harder simulated data
caption work

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses3.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures. The units are defined by the critical
density, so that a mass of $\pi$ units would have an Einstein radius of one arcsecond. To calculate the masses in solar masses, we assumed a flat cosmology with
$\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
$H_0=70$ km/s/Mpc.
\label{fig:masses3}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{N_lens3.pdf}
\caption{The posterior distribution for the number of lens substructures
in the Cosmic Horseshoe system. There is mild evidence in favour of the
hypothesis that $N_{\rm lens} \neq 0$.\label{fig:N_lens3}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{substructures3.pdf}
\caption{The positions of substructures encountered in the MCMC sampling
for the Cosmic Horseshoe; technically a Monte Carlo approximation to the
posterior expected value of the empirical measure of substructure
positions. Unlike Figure~\ref{fig:substructures1}, for the Cosmic Horseshoe
there is little consistency in the positions of the substructures.
\label{fig:substructures3}}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses2.pdf}
\caption{{\revisions
Same as Figure~\ref{fig:masses1}, but for the `harder' simulated dataset.
}
\label{fig:masses2}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{N_lens2.pdf}
\caption{{\revisions
Same as Figure~\ref{fig:N_lens1}, but for the `harder' simulated dataset.
}
\label{fig:N_lens2}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{substructures2.pdf}
\caption{{\revisions
Same as Figure~\ref{fig:substructures1}, but for the `harder' simulated dataset.
The true number of substructures was 10, which also happens to be the posterior
mode. Only five substructures were located within the domain of the image, but
$N_{\rm lens} = 10$ is probable because the spread-out positions of the
m
}
\label{fig:substructures2}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses3.pdf}
\caption{{\revisions Same as Figure~\ref{fig:masses1}, but for the Cosmic Horseshoe.} The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures. The units are defined by the critical
density, so that a mass of $\pi$ units would have an Einstein radius of one arcsecond. To calculate the masses in solar masses, we assumed a flat cosmology with
$\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
$H_0=70$ km/s/Mpc.
\label{fig:masses3}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{N_lens3.pdf}
\caption{{\revisions Same as Figure~\ref{fig:N_lens1}, but for the Cosmic Horseshoe.} The posterior distribution for the number of lens substructures
in the Cosmic Horseshoe system. There is mild evidence in favour of the
hypothesis that $N_{\rm lens} \neq 0$.\label{fig:N_lens3}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{substructures3.pdf}
\caption{{\revisions Same as Figure~\ref{fig:substructures1}, but for the Cosmic Horseshoe.} The positions of substructures encountered in the MCMC sampling
for the Cosmic Horseshoe; technically a Monte Carlo approximation to the
posterior expected value of the empirical measure of substructure
positions. Unlike Figure~\ref{fig:substructures1}, for the Cosmic Horseshoe
there is little consistency in the positions of the substructures.
\label{fig:substructures3}}
\end{center}
\end{figure}
